Data Preparation

### 2019-01-29 Data Preparation.Rmd
save output of transcript summaries

# Save Data
```{r}
save(lists, d_course, d_AoD, d_assessment, d_transcript,
     file = "Output/data_pillar_1.RDATA")
save(lists, d_course, d_AoD, d_assessment, d_transcript,
     d_overview, d_description, d_manual,
     file = "Output/data_pillar_2.RDATA")
```

>>>>

# Save Data
```{r}
save(d_course, d_transcript,
     file = "Output/data_pillar_1.RDATA")
save(lists, d_course, d_AoD, d_assessment, d_transcript,
     d_overview, d_description, d_manual,
     file = "Output/data_pillar_2.RDATA")
```
